---
title: "Pivot Coordinates Notebook"
author: "XuCpeng"
date: "7/23/2021"
output:
  html_notebook: 
    theme: flatly
    highlight: pygments
    toc_depth: 4
---

```{r}
library(readxl)
library(robCompositions)
library(robustHD)
library(compositions)
library("pheatmap")
source('weightPivotCoord.R')
source("WSymmPC.R")
```

```{r}
plotHeatmap <- function(data,main,labels_row_col){
    fig <- pheatmap(data,
                    fontsize = 10, fontsize_row = 7,fontsize_col=8,
                    cluster_row = FALSE,cluster_col=FALSE,
                    main = main,
                    labels_row = labels_row_col,
                    labels_col = labels_row_col)
    return(fig)
}
```

## Hron2021 Test

```{r}
Product <- read_excel("Product_10.5066P9KUH0F6_DATA_Processed.xls",range = "B1:O40",col_names=TRUE)
Product_mx <- as.matrix(Product)

Product_mx<-impAll(Product_mx)

D_p <- ncol(Product_mx)
N_p <- nrow(Product_mx)
Rs_p <- matrix(NA,nrow=D_p,ncol=D_p)
Rp_p <- Rs_p
rownames(Rs_p) <- colnames(Product_mx)
colnames(Rs_p) <- colnames(Product_mx)
Rp_wspc_p <- Rs_p
Rs_wspc_p <- Rs_p

for(i in 1:D_p){
    for(j in 1:D_p){
        Z <- pivotCoord(Product_mx[,c(i,j,(1:D_p)[-c(i,j)])],method="symm")
        Rs_p[i,j] <- cor(Z[,1:2],method="spearman")[1,2]
        Rp_p[i,j] <- cor(Z[,1:2],method="pearson")[1,2]
    }
}

for(i in 1:(D_p)){
    for(j in i:D_p){
        if(j==i){
            Rs_wspc_p[i,i] <- 1
            Rp_wspc_p[i,i] <- 1
        }else{
            Z <- weightSymmPivotCoord(Product_mx,pivotvar1 = i,pivotvar2 = j)
            x <- cor(Z[["ws1"]],Z[["ws2"]],method="spearman")
            Rs_wspc_p[i,j] <- x
            Rs_wspc_p[j,i] <- x
            
            x2 <- cor(Z[["ws1"]],Z[["ws2"]],method="pearson")
            Rp_wspc_p[i,j] <- x2
            Rp_wspc_p[j,i] <- x2
        }
    }
}
```

```{r,fig.width=6, fig.height=4}
Rs_wspc_p_fig <- plotHeatmap(Rs_wspc_p, labels_row_col=colnames(Product_mx),
                             main = "Product - Spearman Correlations with W.Symm.pivot coord.")
```

```{r,fig.width=6, fig.height=4}
Rs_p_fig <- plotHeatmap(Rs_p, labels_row_col=colnames(Product_mx),
                             main = "Product - Spearman Correlations with Symm.pivot coord.")
```

## 1. Import Data

```{r}
Datanhao <- read_excel("Datanhao_wspc.xlsx", range = "C1:BH63",col_names = TRUE)
Adaohai <- read_excel("Adaohai7-bdl0005-Zr(AE)_wspc.xlsx", range = "C1:BM34",col_names = TRUE)
Datanhao_mx <- as.matrix(Datanhao)
Adaohai_mx <- as.matrix(Adaohai)
```

## 2. Prepare Data

```{r}
D_d <- ncol(Datanhao_mx)
N_d <- nrow(Datanhao_mx)

D_a <- ncol(Adaohai_mx)
N_a <- nrow(Adaohai_mx)

Rs_d <- matrix(NA,nrow=D_d,ncol=D_d)
Rs_a <- matrix(NA,nrow=D_a,ncol=D_a)

rownames(Rs_d) <- colnames(Datanhao_mx)
colnames(Rs_d) <- colnames(Datanhao_mx)

rownames(Rs_a) <- colnames(Adaohai_mx)
colnames(Rs_a) <- colnames(Adaohai_mx)

Rp_d <- Rs_d
Rp_a <- Rs_a

Rs_wspc_d <- Rs_d
Rs_wspc_a <- Rs_a

Rp_wspc_d <- Rs_d
Rp_wspc_a <- Rs_a

col_labels_d = c(expression("SiO"[2]),expression("TiO"[2]),expression(paste("Al"[2],"O"[3])),
                 expression(paste("Fe"[2],"O"[3])),"MgO","CaO","MnO",
                 expression(paste("K"[2],"O")),expression(paste("P"[2],"O"[5])),
                 colnames(Datanhao_mx)[(10:D_d)])
col_labels_a = c(expression(paste("Al"[2],"O"[3])),expression("SiO"[2]),"CaO",
                 expression(paste("K"[2],"O")),expression("TiO"[2]),
                 expression(paste("Fe"[2],"O"[3])),"MgO",expression(paste("Na"[2],"O")),
                 "MnO",expression(paste("P"[2],"O"[5])),colnames(Adaohai_mx)[(11:D_a)])
```

## 3. Run 

### Pivot Coordinates 

```{r}
pv_a<-robCompositions::pivotCoord(Adaohai_mx)
pv_d<-robCompositions::pivotCoord(Datanhao_mx)
colnames(pv_a)<-colnames(Adaohai_mx)[1:D_a-1]
colnames(pv_d)<-colnames(Datanhao_mx)[1:D_d-1]


write.csv(pv_a,file = "PV_adaohai.csv")
write.csv(pv_d,file = "PV_datanhao.csv")
```


### 3.1 Weight pivot coordinates (Not Finished)

```{r}
res_d <-weightPivotCoord(Datanhao_mx, pow = 2, pivotvar = 1)
res_a <- weightPivotCoord(Adaohai_mx, pow = 2, pivotvar = 1)

WPC_d <- res_d[['WPC']]
colnames(WPC_d) <- colnames(Datanhao_mx)[1:D_d-1]
w_d <- res_d[['w']]

WPC_a <- res_a[['WPC']]
colnames(WPC_a) <- colnames(Adaohai_mx)[1:D_a-1]
w_a <- res_a[['w']]

#tmp2=PLR(Adaohai_mx)
```

```{r}
write.csv(WPC_d,file = "WPC_datanhao.csv")
write.csv(WPC_a,file = "WPC_adaohai.csv")
```

### 3.2 Symmetric pivot coordinates

```{r}
for(i in 1:D_d){
    for(j in 1:D_d){
        Z <- pivotCoord(Datanhao_mx[,c(i,j,(1:D_d)[-c(i,j)])],method="symm")
        Rs_d[i,j] <- cor(Z[,1:2],method="spearman")[1,2]
        Rp_d[i,j] <- cor(Z[,1:2],method="pearson")[1,2]
    }
}

for(i in 1:D_a){
    for(j in 1:D_a){
        Z <- pivotCoord(Adaohai_mx[,c(i,j,(1:D_a)[-c(i,j)])],method="symm")
        Rs_a[i,j] <- cor(Z[,1:2],method="spearman")[1,2]
        Rp_a[i,j] <- cor(Z[,1:2],method="pearson")[1,2]
    }
}
```

```{r}
# spearman
write.csv(Rs_d,file = "Rs_datanhao.csv")
write.csv(Rs_a,file = "Rs_adaohai.csv")

# pearson
write.csv(Rp_d,file = "Rp_datanhao.csv")
write.csv(Rp_a,file = "Rp_adaohai.csv")
```

### 3.3 **Weighted** Symmetric pivot coordinates

#### W.Symm.PC Test:

```{r}
expendituresTop2=expenditures[1:2,1:3]
A = (1/(sqrt(12-6*sqrt(3))))

A*log(expendituresTop2[,1]
      /((expendituresTop2[,2]^(2-sqrt(3)))*(expendituresTop2[,3]^(-1+sqrt(3)))))

A*log(expendituresTop2[,2]
      /((expendituresTop2[,1]^(2-sqrt(3)))*(expendituresTop2[,3]^(-1+sqrt(3)))))

weightSymmPivotCoord(expendituresTop2)
```

#### W.Symm.PC on Datanhao and Adaohai datasets:

```{r}
for(i in 1:(D_d)){
    for(j in i:D_d){
        if(j==i){
            Rs_wspc_d[i,i] <- 1
            Rp_wspc_d[i,i] <- 1
        }else{
            Z <- weightSymmPivotCoord(Datanhao_mx,pivotvar1 = i,pivotvar2 = j)
            x <- cor(Z[["ws1"]],Z[["ws2"]],method="spearman")
            Rs_wspc_d[i,j] <- x
            Rs_wspc_d[j,i] <- x
            
            x2 <- cor(Z[["ws1"]],Z[["ws2"]],method="pearson")
            Rp_wspc_d[i,j] <- x2
            Rp_wspc_d[j,i] <- x2
        }
    }
}

for(i in 1:(D_a)){
    for(j in i:D_a){
        if(j==i){
            Rs_wspc_a[i,i] <- 1
            Rp_wspc_a[i,i] <- 1
        }else{
            Z <- weightSymmPivotCoord(Adaohai_mx,pivotvar1 = i,pivotvar2 = j)
            x <- cor(Z[["ws1"]],Z[["ws2"]],method="spearman")
            Rs_wspc_a[i,j] <- x
            Rs_wspc_a[j,i] <- x
            
            x2 <- cor(Z[["ws1"]],Z[["ws2"]],method="pearson")
            Rp_wspc_a[i,j] <- x2
            Rp_wspc_a[j,i] <- x2
        }
    }
}
```

```{r}
# spearman
write.csv(Rs_wspc_d,file = "Rs_wspc_datanhao.csv")
write.csv(Rs_wspc_a,file = "Rs_wspc_adaohai.csv")
# pearson
write.csv(Rp_wspc_d,file = "Rp_wspc_datanhao.csv")
write.csv(Rp_wspc_a,file = "Rp_wspc_adaohai.csv")
```

## 4. Plot

### 4.1 Datanhao: Pearson correlation coefficients with symmetric pivot coordinates

```{r,fig.width=12, fig.height=8}
Rp_d_fig <- plotHeatmap(Rp_d,
                        main = "Datanhao - Pearson Correlations with Symm.pivot coord.",
                        labels_row_col = col_labels_d)
```

```{r}
ggsave(Rp_d_fig, filename="Datanhao-Pearson Correlations with Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.2 Datanhao: **Weighted** Pearson correlation coefficients with symmetric pivot coordinates

```{r,fig.width=12, fig.height=8}
Rp_wspc_d_fig <- plotHeatmap(Rp_wspc_d, 
                             main = "Datanhao - Pearson Correlations with W.Symm.pivot coord.",
                             labels_row_col = col_labels_d)
```

```{r}
ggsave(Rp_wspc_d_fig, filename="Datanhao-Pearson Correlations with W_Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.3 Adaohai: Pearson correlation coefficients with symmetric pivot coordinates

```{r,fig.width=12, fig.height=8}
Rp_a_fig <- plotHeatmap(Rp_a,
                        main="Adaohai - Pearson Correlations with Symm.pivot coord.",
                        labels_row_col = col_labels_a)
```

```{r}
ggsave(Rp_a_fig, filename="Adaohai-Pearson Correlations with Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.4 Adaohai: **Weighted** Pearson correlation coefficients with symmetric pivot coordinates

```{r,fig.width=12, fig.height=8}
Rp_wspc_a_fig <- plotHeatmap(Rp_wspc_a,
                             main = "Adaohai - Pearson Correlations with W.Symm.pivot coord.",
                             labels_row_col = col_labels_a)
```

```{r}
ggsave(Rp_wspc_a_fig, filename="Adaohai-Pearson Correlations with W_Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

---

### 4.5 Datanhao: Spearman correlation coefficients with symmetric pivot coordinates

```{r,fig.width=6, fig.height=4}
Rs_d_fig <- plotHeatmap(Rs_d,main = "Datanhao - Spearman Correlations with Symm.pivot coord.",labels_row_col = col_labels_d)
```

```{r}
ggsave(Rs_d_fig, filename="Datanhao-Spearman Correlations with Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.6 Datanhao: **Weighted** Spearman correlation coefficients with symmetric pivot coordinates

```{r,fig.width=6, fig.height=4}
Rs_wspc_d_fig <- plotHeatmap(Rs_wspc_d,main = "Datanhao - Spearman Correlations with W.Symm.pivot coord.",labels_row_col = col_labels_d)
```

```{r}
ggsave(Rs_wspc_d_fig, filename="Datanhao-Spearman Correlations with W_Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.7 Adaohai: Spearman correlation coefficients with symmetric pivot coordinates

```{r,fig.width=6, fig.height=4}
Rs_a_fig <- plotHeatmap(Rs_a,main="Adaohai - Spearman Correlations with Symm.pivot coord.",labels_row_col = col_labels_a)
```

```{r}
ggsave(Rs_a_fig, filename="Adaohai-Spearman Correlations with Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

### 4.8 Adaohai: **Weighted** Spearman correlation coefficients with symmetric pivot coordinates

```{r,fig.width=6, fig.height=4}
Rs_wspc_a_fig <- plotHeatmap(Rs_wspc_a,main = "Adaohai - Spearman Correlations with W.Symm.pivot coord.",labels_row_col = col_labels_a)
```

```{r}
ggsave(Rs_wspc_a_fig, filename="Adaohai-Spearman Correlations with W_Symm_pivot coord.tiff",
       dpi = 320,units="px",width = 3840,height = 2160)
```

